\chapter{Other Nonfunctional Requirements}

\section{Performance Requirements}
\begin{itemize}
	\item The drones will be able to communicate with the ranger in less than 3 seconds with notifications or status updates.
	\item The system will be able to identify objects in less than 2 seconds and notify the ranger if needed.
	\item The drones will be able to change flight paths before within 2 seconds of spotting an object that it will collide with.
	\item The drone will be able to process the information and pin it on the map within a 3 second standstil period.
\end{itemize}

\section{Safety Requirements}
\begin{itemize}
	\item The drone will take off and land by automated mechanisms to ensure ranger safety.
	\item The drone will keep a safe distance from the ranger at all times while in the air.
	\item The drone will ignore further commands and return to the landing pad if the battery falls below a certain level.
	\item The drone will return to the landing pad if it loses a connection to the ranger to prevent damage to the drone.
\end{itemize}

\section{Security Requirements}
\begin{itemize}
	\item The drone will encrypt its stored data to ensure that if a drone is lost or stolen no sentitive information can be leaked.
	\item The drone will only accept commands from an authenticated entity to minimize the risk of hijacking or malicious actions, safety procedure will be followed in the event that the drone is unable to receive any commands after a set period (I.e. 30 seconds).
	\item The ranger will constantly be sending and receiving communication from the drone across a wireless signal, therefore all transmitted information will require at least 256-bit encryption to ensure no senstive information is leaked to potential evildoers.
\end{itemize}

\section{Software Quality Attributes}
\subsection {Reliability}
\begin{itemize}
	\item The drone will act out its set programming in an accurate and consistent manner and revert to default behaviour patterns when no instructions received.  
	\item Ranger inputs received will be processed correctly and then execute in a manner which is expected. Unrecognised inputs or corrupt data received shall be ignored as only valid input is accepted.
\end{itemize}

\subsection {Availability}
\begin{itemize}
	\item The drone will actively listen to inputs from the ranger even while performing other tasks as commands from the ranger are prioritised. 
	\item The drone will not be impeded or overloaded by its subsystem's performance demands thus maintaining availability. 
	\item The drone will drop a pin if the drone gets damaged. 
\end{itemize}

\subsection {Usability}
\begin{itemize}
	\item The application will have an intuitive UI with basic commands and modes of operation. Different modes of operations can be activated  by the ranger without requiring futher inputs as its executed autonomously 
\end{itemize}

